Enhancing Depth Estimation with Iterative Stereo-LiDAR Fusion: An Application of the Papoulis-Gerchberg Algorithm\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-02-29 paper/main.tex
Post-proc section modified

\subsubsection{LiDAR Null Mask}

@@

%% cite the paper from kuzucu-elvan
%% add another image explaining the plan
\subsubsection{Our Approach}

@@

\paragraph{Evaluated PG for Our Work}

\subsection{Post-Proc}

The post-processing consinst of two major parts

@@

@@

>>>>

\subsubsection{LiDAR Null Mask} \label{lidar-null-mask}

@@

%% cite the paper from kuzucu-elvan
%% add another image explaining the plan
\paragraph{Our Approach}

@@

% \paragraph{Evaluated PG for Our Work}

\subsection{Post-Processing}

The post-processing phase is designed to refine the fused depth data, ensuring its accuracy and consistency. This phase is divided into two primary components:

@@

A key step involves utilizing the stereo null mask to identify and eliminate any trivial or less reliable data that was introduced during the data augmentation process. Specifically, depth estimations that fall within areas masked by the stereo null mask are removed from the final depth frame. This mask effectively delineates regions where the stereo data lacked sufficient information, ensuring that only depth data with a high confidence level, either directly measured or accurately estimated, is retained in the final output.

\subsubsection{Enhancement and Smoothing}

To further improve the quality of the fused depth maps, an enhancement and smoothing process is applied. This involves the use of filtering techniques to reduce noise and smooth out rough edges, enhancing the overall visual quality of the depth map. Techniques such as Gaussian smoothing or median filtering can be particularly effective in achieving a more coherent depth representation, especially in areas where the fusion of stereo and LiDAR data may produce discontinuities or artifacts.

\subsubsection{Final Depth Consistency Check}

Another critical component of the post-processing phase is the final depth consistency check. This step involves comparing the processed depth map against the original LiDAR and stereo data to identify and correct any discrepancies. Discrepancy correction can be performed through a combination of automated threshold-based adjustments and manual inspections, ensuring that the final depth map faithfully represents the real-world scene.

\subsubsection{Edge Sharpening}

Lastly, edge sharpening techniques are applied to restore and emphasize the definition of edges that may have been softened during the smoothing process. This is particularly important for maintaining the structural integrity of objects within the scene, allowing for clear delineation between different entities and the background. Techniques such as unsharp masking or adaptive sharpening filters can be employed to enhance edge clarity without introducing noise or artifacts.

@@

\vspace{12pt}
\color{red}
Tüm referanslar kontrol edilmeli (label referansları dahil)
